### 2021-06-21 src/paper/report.tex
Put comments back in.

Modelling a population of agents according to actual demographic characteristics means
that we can use a wide array of data to identify and estimate the model's many
parameters.\footnote{See section~\ref{sec:data_and_parameters} of the supplementary
materials for an overview.} Contact diaries yield pre-pandemic distributions of contacts
for different contact types and their assortativity by age group. Mobility data is used
to model the evolution of work contacts. School and daycare policies can be incorporated
directly from official directives. Administrative records on the number of tests,
vaccinations by age and region, and the prevalence of virus strains are generally
available. Surveys may ask about test offers, propensities to take them up, and past
tests. Other studies' estimates of the seasonality of infections can be incorporated
directly. The remaining parameters---most notably, these include infection probabilities
by contact network and the effects of NPIs, see Supplementary
Material~\ref{subsec:estimated_params}---will be chosen numerically so that the model
matches features of the data \citep[see][for the general method, also described in
Supplementary Material \ref{sec:model}]{McFadden1989}.\comment[id=HM]{Make reference
more specific once Appendix has new structure} In our application, we keep the number of
free parameters low in order to avoid overfitting. The data features to be matched
include official case numbers for each age group and region, deaths, and the share of
the B.1.1.7 strain.

>>>>

Modelling a population of agents according to actual demographic characteristics means
that we can use a wide array of data to identify and estimate the model's many
parameters.\footnote{See section~\ref{sec:data_and_parameters} of the supplementary
materials for an overview.} Contact diaries yield pre-pandemic distributions of contacts
for different contact types and their assortativity by age group. Mobility data is used
to model the evolution of work contacts. School and daycare policies can be incorporated
directly from official directives. Administrative records on the number of tests,
vaccinations by age and region, and the prevalence of virus strains are generally
available. Surveys may ask about test offers, propensities to take them up, and past
tests. Other studies' estimates of the seasonality of infections can be incorporated
directly. The remaining parameters---most notably, these include infection probabilities
by contact network and the effects of NPIs, see Supplementary
Material~\ref{subsec:estimated_params}---will be chosen numerically so that the model
matches features of the data \citep[see][for the general method, also described in
Supplementary Material \ref{sec:model}]{McFadden1989}.\comment[id=HM]{Make referencemore
specific once Appendix has new structure} In our application, we keep the number of free
parameters low in order to avoid overfitting. The data features to be matched include
official case numbers for each age group and region, deaths, and the share of the B.1.1.7
strain.
